Efficient Methods for Solving String Constraints with Bounded Repetition

### 2023-04-23 2023-1-19/sections/implementation.tex
revise implementation

Table \ref{tab:results_all} summarizes the results that demonstrate OstrichCEA's superior performance, solving most instances and outperforming most competing solvers. OstrichCEA is \textbf{0.98}\mult{} faster than Z3str3RE (with timeouts), \textbf{1.52}\mult{} faster than Z3Seq, \textbf{2.23}\mult{} faster than Ostrich, \textbf{2.26}\mult{} faster than Z3-Trau, \textbf{3.08}\mult{} faster than Z3str3 and \textbf{3.11}\mult{} faster than CVC5. Note that CVC5\cite{cvc5} yielded 5370 timeouts(11\% of all instances), and Z3str3\cite{z3str3} yielded 6139 timeouts(12\% of all instances), which is much more than other solvers. Both CVC5 and Z3str3 are DPLL(T)-based solvers. It seems that almost 10\% of the benchmarks we used seem unsuitable for them. Z3-trau\cite{z3trau} yielded 21,152 unknowns because it does not support \verb|re.diff|. Z3-trau\cite{z3trau} yielded 6673 crashes (13\% of the instances) and 1233 soundness errors (2\% of the instances), which is a large portion. Z3-based solvers Z3str3 yielded 38 soundness errors, Z3seq\cite{z3seq} yielded 51 soundness errors and Z3str3RE\cite{z3str3re} yielded 39 soundness error. Most of them are due to the mistake formalization of the backslash character. OstrichCEA resulted 5 unknowns because it reached the maximum threshold of limited memory 2GB.

@@

\subsection{Detailed Evaluation}
The detailed results for the \textbf{AutomatArk} benchmark are presented in Figure \ref{fig:cactus_automatrk} and Table \ref{tab:results_automatrk}. OstrichCEA solved the most \emph{unsat} instances. Z3str3RE solved the most \emph{sat} instances. Ostrich solved the greatest number of instances, while Z3str3RE used the least time with timeouts.\newline
The detailed results for the \textbf{Redos} benchmark are presented in Figure \ref{fig:cactus_redos} and Table \ref{tab:results_redos}. OstrichCEA solved the most \emph{sat} and \emph{unsat} benchmark. Z3str3RE used the least time in total. \newline 
The detailed results for the \textbf{RegexLib} benchmark are presented in Figure \ref{fig:cactus_regexlib} and Table \ref{tab:results_regexlib}. Ostrich solved the most \emph{unsat} benchmarks. OstrichCEA solved the most \emph{sat} benchmarks. OstrichCEA solved the most benchmarks in total.  Z3str3RE used the least time in total. \newline
The detailed results for the \textbf{StackOverflow} benchmark are presented in Figure \ref{fig:cactus_stackoverflow} and Table \ref{tab:results_stackoverflow}. OstrichCEA solved the most benchmarks and used the least time in total.\newline
\begin{figure}
  \centering
  \subimport{figures}{cactus_plot_automatark.tex}
  \caption{The plot of a cactus graph depicting a comprehensive evaluation of the performance of the AutomatArk benchmark.}
  \label{fig:cactus_automatrk}
\end{figure}
\begin{table}
  \subimport{tables}{table_automatark.tex}
  \caption{Detailed results for the AutomatArk benchmark.}
  \label{tab:results_automatrk}
\end{table}

>>>>

Table \ref{tab:results_all} summarizes the results that demonstrate OstrichCEA's superior performance, solving the most significant number of instances and outperforming most competing solvers. Including timeouts, OstrichCEA is \textbf{1.52}\mult{} faster than Z3Seq, \textbf{2.23}\mult{} faster than Ostrich, \textbf{2.26}\mult{} faster than Z3-Trau, \textbf{3.08}\mult{} faster than Z3str3, \textbf{3.11}\mult{} faster than CVC5 and close to Z3str3RE with \%2 speed loss . Note that CVC5\cite{cvc5} yielded 5370 timeouts(11\% of all instances), and Z3str3\cite{z3str3} yielded 6139 timeouts(12\% of all instances), which is much more than other solvers. Both CVC5 and Z3str3 are DPLL(T)-based solvers. It seems that almost 10\% of the benchmarks we used seem unsuitable for them. Z3-trau\cite{z3trau} yielded 21,152 unknowns because it does not support \verb|re.diff|. Z3-trau\cite{z3trau} yielded 6673 crashes (13\% of the instances) and 1233 soundness errors (2\% of the instances), which is a large portion. Z3-based solvers Z3str3 yielded 38 soundness errors, Z3seq\cite{z3seq} yielded 51 soundness errors and Z3str3RE\cite{z3str3re} yielded 39 soundness error. Most of them are due to the mistake formalization of the backslash character. OstrichCEA resulted 5 unknowns because it reached the maximum threshold of limited memory 2GB.

@@

\subsection{Detailed Evaluation}
The detailed results for the \textbf{AutomatArk} benchmark are presented in Figure \ref{fig:cactus_automatrk} and Table \ref{tab:results_automatrk}. OstrichCEA solved the most \emph{unsat} instances. Z3str3RE solved the most \emph{sat} instances. Ostrich solved the greatest number of instances, while Z3str3RE used the least time with timeouts.\newline
The detailed results for the \textbf{Redos} benchmark are presented in Figure \ref{fig:cactus_redos} and Table \ref{tab:results_redos}. OstrichCEA solved the most instances on both tracks of \emph{sat} and \emph{unsat}. Including timeouts, OstrichCEA is \textbf{4.4}\mult{} faster than CVC5, \textbf{3.74}\mult{} faster than Ostrich, \textbf{2.09}\mult{} faster than Z3str3, \textbf{5.40}\mult{} faster than Z3seq, \textbf{2.49}\mult{} faster than Z3-Trau and close to Z3str3RE with \%20 speed loss. \newline 
The detailed results for the \textbf{RegexLib} benchmark are presented in Figure \ref{fig:cactus_regexlib} and Table \ref{tab:results_regexlib}. Ostrich solved the most \emph{unsat} instances. OstrichCEA solved the most \emph{sat} instances. In total, OstrichCEA solved the greatest number of instances and was the solver with medium speed. \newline
The detailed results for the \textbf{StackOverflow} benchmark are presented in Figure \ref{fig:cactus_stackoverflow} and Table \ref{tab:results_stackoverflow}. OstrichCEA solved the most instances on both tracks of \emph{sat} and \emph{unsat} and was the faster solver.\newline Including timeouts, OstrichCEA is \textbf{3.98}\mult{} faster than CVC5, \textbf{2.63}\mult{} faster than Ostrich, \textbf{2.19}\mult{} faster than Z3str3, \textbf{1.59}\mult{} faster than Z3seq, \textbf{1.28}\mult{} faster than CVC5 and \textbf{1.47}\mult{} to Z3str3RE. \newline
\begin{figure}
  \centering
  \subimport{figures}{cactus_plot_automatark.tex}
  \caption{The plot of a cactus graph depicting a comprehensive evaluation of the performance of the AutomatArk benchmark.}
  \label{fig:cactus_automatrk}
\end{figure}
\begin{table}
  \subimport{tables}{table_automatark.tex}
  \caption{Detailed results for the AutomatArk benchmark.}
  \label{tab:results_automatrk}
\end{table}
